Airline Customer Satisfaction - Group 17

### 2025-04-04 Draft Business Analytics Assignment Group 17.Rmd
Updated Chapter 3

```{r}
data_subset <- data %>%
  select(Satisfaction, Flight.Service, Flight.Entertainment, Digital.Service, Comfort.Service)

@@

# Top contributors for PC1–PC12
top_vars <- apply(abs(loadings[, 1:12]), 2, function(x) names(sort(x, decreasing = TRUE)[1:5]))
print(top_vars)
```
PC1 – In-Flight Amenities & Comfort
Driven by Flight.Entertainment, Comfort.Service, In.flight.Entertainment, Flight.Service, and Cleanliness. This component captures the overall in-flight experience focused on comfort and entertainment.

PC2 – Digital & Booking Experience
Influenced by Ease.of.Online.Booking, Digital.Service, and In.flight.Wifi.Service. It represents passengers’ interaction with digital services before and during the flight.

@@

PC9 – Comfort in Long Trips
Includes Leg.Room.Service, Flight.Distance, and Comfort.Service, highlighting comfort needs for longer or more frequent flights.

PC10 – In-Flight Consumables
Composed of On.board.Service, Flight.Service, and Food.and.Drink, focusing on passengers’ satisfaction with in-flight consumables.

@@

```{r}
# Create copy of dataset for the purpose of classification only, convert to factor
data_clsf <- as.data.frame(lapply(data, as.factor))

@@

```{r}
install.packages("ranger")
library(ranger)
```

@@

```{r}
training_signif <- training %>% subset(select = -c(Departure.Delay, Arrival.Delay, Flight.Distance, 
                                                  In.flight.Wifi.Service, Food.and.Drink, 
                                                  In.flight.Entertainment, Age_Range, Distance_Group,
                                                  Flight.Service, Flight.Entertainment, 
                                                  Comfort.Service, Digital.Service, 
                                                  Flight.Distance.log.z, Age.log.z))

@@

```{r}
print("Confusion matrix for Logistic Regression")
CrossTable(testing$Satisfaction, pred_class,
           prop.chisq = FALSE,
           prop.c = FALSE,
           prop.r = FALSE,
           prop.t = FALSE,
           dnn = c("Actual Satisfaction", "Predicted Satisfaction"))
```

>>>>

```{r}
data_subset <- data %>%
  select(Satisfaction, In.flight.service, Flight.Entertainment, Pre.flight.service, Comfortability)

@@

# Top contributors for PC1–PC12
top_vars <- apply(abs(loadings[, 1:12]), 2, function(x) names(sort(x, decreasing = TRUE)[1:5]))
print(top_vars)
```
PC1 – In-Flight Amenities & Comfort
Driven by Flight.Entertainment, Comfortability, In.flight.Entertainment, In.flight.service, and Cleanliness. This component captures the overall in-flight experience focused on comfort and entertainment.

PC2 – Digital & Booking Experience
Influenced by Ease.of.Online.Booking, Pre.flight.service, and In.flight.Wifi.Service. It represents passengers’ interaction with digital services before and during the flight.

@@

PC9 – Comfort in Long Trips
Includes Leg.Room.Service, Flight.Distance, and Comfortability, highlighting comfort needs for longer or more frequent flights.

PC10 – In-Flight Consumables
Composed of On.board.Service, In.flight.service, and Food.and.Drink, focusing on passengers’ satisfaction with in-flight consumables.

@@

```{r}
# Create copy of dataset for the purpose of classification only, convert to factor
data_clsf <- data %>%
      mutate(across(-c(ID, Age, Flight.Distance, Departure.Delay, Arrival.Delay, 
                   Departure.Delay.Duration,
                   Arrival.Delay.Duration, Arrival.Delay.Duration.log, Arrival.Delay.Duration.log.z,
                   Departure.Delay.Duration.log, Departure.Delay.Duration.log.z, Flight.Distance.log,
                   Flight.Distance.log.z, Age.log, Age.log.z), as.factor))

@@

```{r}
# install.packages("ranger")
library(ranger)
```

@@

```{r}
training_signif <- training %>% subset(select = -c(Departure.Delay, Arrival.Delay, Flight.Distance, 
                                                  In.flight.Wifi.Service, Food.and.Drink, 
                                                  In.flight.Entertainment, Age_Range, Distance_Group,
                                                  In.flight.service, Flight.Entertainment, 
                                                  Comfortability, Pre.flight.service, 
                                                  Flight.Distance.log.z, Age.log.z))

@@
